Introduction to Structural Causal Models

### 2021-05-21 presentation_video.Rmd
lecture

---
title: "Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "5/11/2021"
citation_package: --biblatex
bibliography: [ref.bib]
#csl: ieee.csl
output: 
  beamer_presentation:
    theme: Madrid
header-includes:
- \definecolor{UBCblue}{rgb}{0.04706, 0.13725, 0.26667}
- \usecolortheme[named=UBCblue]{structure}
---

@@

- Conflict whether to use **graphs** or not and to use **parameters** in SEM
* SEM is a parametric model used in applied sciences 
* A Bayesian causal network (BCN) use conditional probabilities instead of functions 
* PO is mostly equivalent but has not graphical framework
* SCM and PO are only frameworks that allow for counterfactuals
- Every SCM has the same information as respective probabilisitc model + more (DGP)
- SCMs can derive potential outcomes but PO cannot derive SCMs

@@

* Foundations of SCMs 
  * Assumptions 
  * Comparing Causal Tools 
* Pearl's Causal Hierachy
  * Prediction 
  * Intervention 
  * Counterfactuals 
* Graphical Models
* **Causality and Time**

>>>>

---
title: "Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "May 2021"
citation_package: --biblatex
bibliography: [ref.bib]
#csl: ieee.csl
output: 
  beamer_presentation:
    theme: Madrid
header-includes:
- \definecolor{UBCblue}{rgb}{0.04706, 0.13725, 0.26667}
- \usecolortheme[named=UBCblue]{structure}
---

@@

- Conflict whether to use **graphs** or not and to use **parameters** in SEM
* SEM is a parametric model used in applied sciences 
* A Bayesian causal network (BCN) use conditional probabilities instead of functions 
* PO is mostly equivalent but has not graphical framework
* SCM and PO are only frameworks that allow for counterfactuals
- Every SCM has the same information as respective probabilistic model + more (DGP)
- SCMs can derive potential outcomes but PO cannot derive SCMs

@@

* Foundations of SCMs 
  * Assumptions 
  * Comparing Causal Tools 
* Pearl's Causal Hierarchy
  * Prediction 
  * Intervention 
  * Counterfactuals 
* Graphical Models
* **Causality and Time**
